---
title: "Plots in Comparison of platforms for testing antibodies to Chlamydia trachomatis antigens: data from the Democratic Republic of the Congo and Togo"
author: "Jessica Hoehner"
date: "Last compiled `r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    keep_md: yes
    theme: "journal"
    highlight: "default"
    toc: no
---

```{r setup, include=FALSE, message=FALSE, echo=FALSE}

pacman::p_load(
  "here", "readr", "readxl",
  "janitor", "tidyverse", "assertr",
  "ggplot2", "tmap")

# read in data
files <- list(
  drc1_MBA_clean = here("plot/input/drc1_MBA_cleanobs.csv"),
  togoMBAc_41_clean = here("plot/input/togoMBAc_41_cleanobs.csv"),
  drc1_MBA_obs = here("plot/input/drc1_MBA_obs.csv"),
  togoMBAc_41_obs = here("plot/input/togoMBAc_41_obs.csv"),
  drc1_MBA_mod = here("plot/input/drc1_MBA_model_ests.csv"),
  togoMBAc_41_mod = here("plot/input/togoMBAc_41_model_ests.csv"))

```

## Where do our data come from? {-}

The data in our sample come from communities in the Democratic Republic of the 
Congo (DRC) and the Togolese Republic (Togo). 

Here we use `tmap` to create an interactive map with the DRC in blue and Togo in dark green. To make this 
plot more accessible to all users, we have chosen color-blind friendly shades of
these colors and style options for the map overall using [colorbrewer2.org]("https://colorbrewer2.org") 
and options available in `tmap`.

```{r map, fig.height=5, fig.width=4, message=FALSE, warning=FALSE}
tmap_mode("view")
data("World")

Africa = World[World$continent == "Africa", ]

tm_shape(Africa) + 
  tm_polygons() +
  tm_shape(World, filter = World$name == "Dem. Rep. Congo" | World$name == "Togo") +
  tmap_options(max.categories = 2) +
  tm_polygons("name", palette = c("#4575b4", "#006837"), legend.show = FALSE) +
  tm_style("col_blind")

```

## Figure 2: Age vs Antibody Titre {-}

```{r titreplotssetup, message=FALSE, include=FALSE}

titre_df_drc <- as.data.frame(read_csv(files$drc1_MBA_clean, 
                                       col_names = TRUE, na = "NA")) %>%
    clean_names() %>%
    transmute(age = as.numeric(age),
              titre = as.numeric(titre),
              sero_pos = as.factor(sero_pos)) %>%
  verify(ncol(.) == 3)  %>%
  verify(is.na(.) == FALSE)

titre_df_togo <- as.data.frame(read_csv(files$togoMBAc_41_clean, 
                                        col_names = TRUE, na = "NA")) %>%
    clean_names() %>%
    transmute(age = as.numeric(age),
              titre = as.numeric(titre),
              sero_pos = as.factor(sero_pos)) %>%
  verify(ncol(.) == 3)  %>%
  verify(is.na(.) == FALSE)

```

Here is an example of the plot created using `ggplot2` and data from Manono, DRC 
and Keran, Togo for the antibody response to the immunodominant antigen produced 
during infection with _Chlamydia_ _trachomatis_, PgP3, measured by Multiplex 
Bead Assay (MBA).

```{r titreplots_example, fig.height=4, fig.width=6, message=FALSE, warning=FALSE}

ggplot(titre_df_drc, aes(age, titre, group = age)) +
  geom_boxplot(aes(age, titre),
    color = "#4575b4",
    fill = "#4575b4",
    alpha = 0.2,
    outlier.colour = "white") +
  theme_classic() +
  geom_jitter(
    na.rm = FALSE,
    width = 0.3) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_y_log10(
    breaks = c(1, 1500, 15000, 150000),
    labels = c(1, 1500, 15000, 150000),
    limits = c(1, 150000)) +
  xlab("Age (Years)") +
  ylab("log10 Antibody Titre") +
  ggtitle("Manono: DRC: Age vs Antibody Titre (log10)") +
  coord_trans(y = scales::exp_trans()) +
  theme(
    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20))


ggplot(titre_df_togo, aes(age, titre, group = age)) +
  geom_boxplot(aes(age, titre),
    color = "#006837",
    fill = "#006837",
    alpha = 0.2,
    outlier.colour = "white") +
  theme_classic() +
  geom_jitter(
    na.rm = FALSE,
    width = 0.3) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_y_log10(
    breaks = c(1, 1500, 15000, 150000),
    labels = c(1, 1500, 15000, 150000),
    limits = c(1, 150000)) +
  xlab("Age (Years)") +
  ylab("log10 Antibody Titre") +
  ggtitle("Keran, Togo: Age vs Antibody Titre (log10)") +
  coord_trans(y = scales::exp_trans()) +
  theme(
    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20))

```

## Figure 3: Age vs Seroconversion Rate (SCR) Estimates and Observed Seroprevalence {-}

```{r agescr_prep, message=FALSE, include=FALSE}

obs_df_drc <- as.data.frame(read_csv(files$drc1_MBA_obs, 
                                 col_names = TRUE, na = "NA")) %>%
  clean_names() %>%
  verify(ncol(.) == 5 & nrow(.) == 9) %>%
  verify(is.na(.) == FALSE) %>%
  transmute(
    med = med,
    low_95 = low_95,
    high_95 = high_95,
    age = age,
    age_bins_mid = age_bins_mid,
    rownum = row_number())

mod_df_drc <- as.data.frame(read_csv(files$drc1_MBA_mod, 
                                 col_names = TRUE, na = "NA")) %>%
  clean_names() %>%
  verify(ncol(.) == 5 & nrow(.) == 46) %>%
  verify(is.na(.) == FALSE) %>%
  transmute(
    medest = medest,
    low95_est = low95_est,
    high95_est = high95_est,
    age_seq = age_seq,
    rownum = row_number())

plot_df_drc <- full_join(obs_df_drc, mod_df_drc, by = "rownum")

obs_df_togo <- as.data.frame(read_csv(files$togoMBAc_41_obs, 
                                 col_names = TRUE, na = "NA")) %>%
  clean_names() %>%
  verify(ncol(.) == 5 & nrow(.) == 9) %>%
  verify(is.na(.) == FALSE) %>%
  transmute(
    med = med,
    low_95 = low_95,
    high_95 = high_95,
    age = age,
    age_bins_mid = age_bins_mid,
    rownum = row_number())

mod_df_togo <- as.data.frame(read_csv(files$togoMBAc_41_mod, 
                                 col_names = TRUE, na = "NA")) %>%
  clean_names() %>%
  verify(ncol(.) == 5 & nrow(.) == 46) %>%
  verify(is.na(.) == FALSE) %>%
  transmute(
    medest = medest,
    low95_est = low95_est,
    high95_est = high95_est,
    age_seq = age_seq,
    rownum = row_number())

plot_df_togo <- full_join(obs_df_togo, mod_df_togo, by = "rownum")

```

Using `ggplot2`and data from the same communities as above, we can also examine 
the relationship between observed seroprevalence in each age group, estimates of 
median SCR, and age. 

The points represent the median seroprevalence observed within each age group, 
the solid line represents the estimated median SCR by age, and the light bands 
around the line and points represent the 95% credible intervals around the 
estimates of SCR.

```{r agescr_example, fig.height=4, fig.width=6, warning=FALSE}

ggplot(plot_df_drc, aes(age, med, age_bins_mid)) +
  geom_pointrange(aes(
    ymin = low_95,
    ymax = high_95)) +
  geom_errorbar(aes(
    ymin = low_95,
    ymax = high_95),
  colour = "black",
  width = .1,) +
  geom_line(aes(age_seq, medest),
    color = "#4575b4",) +
  geom_ribbon(aes(age_seq,
    ymin = low95_est,
    ymax = high95_est ),
  fill = "#4575b4",
  alpha = 0.2) +
  theme_classic() +
  ylim(0, 1.0) +
  xlab("Age(Years)") +
  ylab("Proportion Seropositive") +
  ggtitle("Manono, DRC: Serocatalytic Modelling") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9)) +
  theme(
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16))

ggplot(plot_df_togo, aes(age, med, age_bins_mid)) +
  geom_pointrange(aes(
    ymin = low_95,
    ymax = high_95)) +
  geom_errorbar(aes(
    ymin = low_95,
    ymax = high_95),
  colour = "black",
  width = .1, ) +
  geom_line(aes(age_seq, medest),
    color = "#006837",) +
  geom_ribbon(aes(age_seq,
    ymin = low95_est,
    ymax = high95_est),
  fill = "#006837",
  alpha = 0.2) +
  theme_classic() +
  ylim(0, 1.0) +
  xlab("Age(Years)") +
  ylab("Proportion Seropositive") +
  ggtitle("Keran, Togo: Serocatalytic Modelling") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9)) +
  theme(
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16))

```












